Predicting instabilities of a tuneable ring laser with an iterative map model

### 2020-11-26 Papers/Journal/Tuneable_Lasers.tex
Edited section 2, and added a reference

\author[1]{Brady Metherall}
\author[2,*]{C. Sean Bohun}

@@

\section{Introduction}
\label{sec:intro}
Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres~\cite{bohun2015, burgoyne2010, yamashita2009}. This ability to vary the frequency leads to applications such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}. Tuneable lasers are usually constructed in a ring with five main components: output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and pump laser. A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}. Due to the high power and short duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.

Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, shao2019, woodward2018}. The two effects of most interest for this paper are wave breaking, and modulation instability. Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}. The shifts in frequencies cause the pulse to become more rectangular in the frequency domain with a linear chirp over most of the pulse. In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the Kerr nonlinearity causing the pulse to interfere with itself. New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, woodward2018}. Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics~\cite{rothenberg1989b}. Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest. However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}. Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}. Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse. This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.

@@

The GNLSE, \eqref{eq:nlse}, has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers a modulation term is typically also added to ensure mode-locking, this yields the master equation of mode-locking (see \cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005}). Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known. See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.

In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity. In Section~\ref{sec:model}, we will briefly review previous iterative mathematical models, then, we will present our own iterative map model. We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system. We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model. We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse. Finally, the concluding thoughts and possible ideas for future work are given in Section~\ref{sec:conclusion}.

\section{Iterative Map Model}
\label{sec:model}
The GNLSE well represents the dynamics in, say, a single optical fibre, it is not completely representative of the underlying physics within a laser cavity. It is assumed in \eqref{eq:nlse} that each process affects the pulse continuously within the cavity. As highlighted by Fig.~\ref{fig:cavity}, this can be a poor assumption as we have discrete components. Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}. Thus, a better model is one where we consider separate, simplified, versions of \eqref{eq:nlse} within each component. These simplified equations can then be solved, giving an analytic expression for how an input pulse will be transformed after passing through each component. We are then able to iteratively send a pulse through each process map to give the total effect of one round trip around the cavity. An iterative map method has the advantage of modelling each component directly, which allows us to portray the geometry of the cavity as it is constructed.

Such a method was first proposed in 1955 by Cutler~\cite{cutler1955} while analyzing a microwave regenerative pulse generator. His method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}. The effects of the nonlinearity would not be considered until Martinez \emph{et al.}~\cite{martinez1984, martinez1985} modelled passively mode-locked lasers. This issue has recently been readdressed by Burgoyne~\cite{burgoyne2014} in the literature for tuneable lasers. In each of these models the effect of each block is described by a transfer function.

Despite the development of discrete, iterative models, several short-comings exist. None of the previous models have contained every component within a laser cavity---either the nonlinearity or the modulation have been omitted. Each component of a tuneable plays a pivotal role and the laser will not function correctly without the inclusion of all of the components. Another drawback is that the functional operations of some of the components used in their models are phenomenological. While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics. Finally, the previous models have been unsuccessful in exhibiting the instabilities described in Section~\ref{sec:intro}.

@@

Repeating this same procedure for the loss, dispersion, and nonlinearity yields
\begin{align}
	L(A) &= (1 - R) \exp( - \alpha L_T )A, \\
	D(A) &= \FTi{\exp( i \omega^2 L_D\beta_2/2 ) \FT{A}}, \\
	F(A) &= A \exp( i \gamma |A|^2 L_f ),
\end{align}
where $R$ is the reflectivity of the output coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \exp( - \alpha L_T )A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and $\mathcal{F}$ denotes the Fourier transform. Finally, we consider the modulation. Here, we assume the pulse is modulated by an electro-optic modulator. This gives the freedom of choosing the profile of the modulation how ever the operator sees fit. For simplicity the representation is taken as the Gaussian
\begin{align}
	M(A) &= \exp( -T^2 / 2 T_M^2 ) A,
	\label{eq:modform}
\end{align}
where $T_M$ is the characteristic width of the modulation. This assumption is not particularly restrictive. Calcaterra and Boldt~\cite{calcaterra2008a} have shown that a sum of Gaussian functions can approximate any square integrable function. Therefore, our solution extends to any continuous, bounded modulation function. Additionally, it is common to use a saturable absorber in place of a modulator. In this case, \eqref{eq:modform} can freely be replaced by~\cite{lapre2019, meng2020}
\begin{align}
	S(A) &= 1 - \frac{q_0}{1 + |A|^2 / P_\text{sat}},
\end{align}
where $q_0$ is the modulation depth, $|A|^2$ is the instantaneous power of the pulse, and $P_\text{sat}$ is the saturation power.

@@

Revisiting the process maps \eqref{eq:gainform}--\eqref{eq:modform} yields the new, non-dimensional, mappings---after dropping the tildes---
\begin{align}
	G(A) &= \left(E_g^{-1} W \left( a E_g \textrm{e}^{E_g}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \nonumber \\
	D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \label{eq:effects} \\
	M(A) &= \exp( -T^2 / 2 ) A, \nonumber
\end{align}
with the four dimensionless parameters, as defined by the values in Table~\ref{tab:values},
\begin{equation}
	\begin{aligned}
		a &= \exp( g_0 L_g ) \sim 8 \times 10^3, & 
		h &= (1 - R) \exp( - \alpha L_T) \sim 0.04, \\
		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, & s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2.
		\label{eq:ndparam}
	\end{aligned}
\end{equation}
Here, $a$ is a measure of the strength of the gain fibre, $h$ is the loss due to absorption and the output coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse. Furthermore, notice that in this non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:ndparam} have their own independent, non-dimensional parameter.

@@

Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity. Thus, we must now consider the order of the components. As we are most interested in the output of the laser cavity, we shall start with the loss. We then pass the pulse through the CFBG followed by the modulator. The pulse then travels through the Er-doped fibre to be amplified, and finally we consider the effect of the nonlinearity. The nonlinearity must immediately follow the gain in this model---this is where the nonlinearity will have the largest effect since this is where the pulse is most energetic. Note, the permutation of the components is indeed important as the process maps do not, in general, commute---unlike the models described in the beginning of Section~\ref{sec:model}. Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power. Functionally we denote one round trip of the cavity by
\begin{align}
	\mathcal{L}(A) = F(G(M(D(L(A))))).
	\label{eq:order}
\end{align}
 The pulse after one complete circuit of the laser cavity is then returned back into the cavity to restart the process. A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity---we are uninterested in the phase due to the nature of experimental measurements. That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$. An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.

@@

\subsection{Linear Solution}
By neglecting the effect of the nonlinearity, that is, $b = 0$, a solution can be found analytically. We proceed by assuming the solution will take the form of a chirped Gaussian. There are a few reasons for this; the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform. Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.

@@

@@

\begin{figure}[tbp]
	\centering
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/Chirp}
		\caption{Chirp.}
		\label{fig:chirp}
	\end{subfigure} \\
	\vspace{3mm}
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/FT}
		\caption{Fourier transform.}
		\label{fig:ft}
	\end{subfigure}
	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for two values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
	\label{fig:chirpft}
\end{figure}

@@

>>>>

\author[1,3]{Brady Metherall}
\author[2,4]{C. Sean Bohun}

@@

\section{Introduction}
\label{sec:intro}

% vary 100 nm ~\cite{bohun2015, burgoyne2010, yamashita2009}

% optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}

% optical frequency metrology, material processing, terahertz generation \cite{oktem2010}

Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres~\cite{bohun2015, burgoyne2010, yamashita2009}. This ability to vary the frequency leads to applications such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}. Tuneable lasers are usually constructed in a ring with five main components: output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and pump laser. A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}. Due to the high power and short duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.

Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, shao2019, woodward2018}. The two effects of most interest for this paper are wave breaking, and modulation instability. Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}. The shifts in frequencies cause the pulse to become more rectangular in the frequency domain with a linear chirp over most of the pulse. In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the Kerr nonlinearity causing the pulse to interfere with itself. New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, woodward2018}. Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest. However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}. Modulation instability causes a degrade into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}. Outside of optics, wave breaking and modulation instability occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}. Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse. This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.

@@

The GNLSE, \eqref{eq:nlse}, has many applications in nonlinear optics and fibre optic communications, however, it is regularly generalized further to include a modulation term in the context of lasers. This is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation. Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known. See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers. The GNLSE well represents the dynamics in, say, a single optical fibre, it is not entirely representative of the underlying physics within a laser cavity. It is assumed in \eqref{eq:nlse} that each process affects the pulse continuously within the cavity. Therefore, the GNLSE, and its derivatives, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during one round trip. Often, this is the case due to the specialized, discrete components.

In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity. In Section~\ref{sec:model}, we will briefly review previous iterative mathematical models, then, we will derive our own iterative map model from \eqref{eq:nlse}. We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system. We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model. We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse. Finally, the concluding thoughts and possible ideas for future work are given in Section~\ref{sec:conclusion}.

\section{Iterative Map Model}
\label{sec:model}
To resolve some of the issues with an `average' model, it is common to use separate GNLSEs for each component and region in the laser, iteratively passing the pulse from one PDE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}. This method allows us to better encapsulate specific dynamics introduced by each component. The main drawback of this method is its extreme computational expense, since a nonlinear PDE must be numerically solved for every component and each of the hundreds of round trips in a given simulation. We can alleviate this computational expense by noticing that each effect is localized to its corresponding component in the cavity: essentially all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}. Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically. We get the benefit of the fine-grain simulation over an `average' model, allowing us to reflect the specific geometry of the cavity, without much additional computational cost.

Iterative map methods have been around since 1955 when Cutler~\cite{cutler1955} analyzed a microwave regenerative pulse generator. Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969} adapted Cutler's method for both AM and FM mode-locked lasers in 1969, and Martinez \emph{et al.}~\cite{martinez1984, martinez1985} incorporated the nonlinearity while modelling passively mode-locked lasers. This method was used for dispersion-tuned actively mode-locked lasers recently by Burgoyne \emph{et al.}~\cite{burgoyne2014}. Each of these models used a prescribed transfer function to describe the effect each component has on the pulse. While the transfer functions are chosen suitably to have the effect observed in the laboratory, they are phenomenologically chosen, and not necessarily obtained from the underlying physics. Furthermore, these methods have not included the effect of every component, lacking the imperative interplay of dispersion, modulation, and nonlinearity---disallowing their models to exhibit modulation instability.

@@

Repeating this same procedure for the loss, dispersion, and nonlinearity yields
\begin{align}
	L(A) &= (1 - R) \exp( - \alpha L_T )A, \\
	D(A) &= \FTi{\exp( i \omega^2 L_D\beta_2/2 ) \FT{A}}, \\
	F(A) &= A \exp( i \gamma |A|^2 L_f ),
\end{align}
where $R$ is the reflectivity of the output coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \exp( - \alpha L_T )A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and $\mathcal{F}$ denotes the Fourier transform. Finally, we consider the modulation. Here, we assume the pulse is modulated by an electro-optic modulator. This gives the freedom of choosing the profile of the modulation how ever the operator sees fit. For simplicity the representation is taken as the Gaussian
\begin{align}
	M(A) &= \exp( -T^2 / 2 T_M^2 ) A,
	\label{eq:modform}
\end{align}
where $T_M$ is the characteristic width of the modulation. This assumption is not particularly restrictive. Calcaterra and Boldt~\cite{calcaterra2008a} have shown that a sum of Gaussian functions can approximate any square integrable function. Therefore, our solution extends to any continuous, bounded modulation function. Additionally, it is common to use a saturable absorber in place of a modulator. In this case, \eqref{eq:modform} can freely be replaced by~\cite{lapre2019, meng2020, oktem2010, woodward2018}
\begin{align}
	S(A) &= 1 - \frac{q_0}{1 + |A|^2 / P_\text{sat}},
\end{align}
where $q_0$ is the modulation depth, $|A|^2$ is the instantaneous power of the pulse, and $P_\text{sat}$ is the saturation power.

@@

Returning to the process maps \eqref{eq:gainform}--\eqref{eq:modform}, we find the non-dimensional mappings to be (after dropping the tildes)
\begin{align}
	G(A) &= \left(E_g^{-1} W \left( a E_g \textrm{e}^{E_g}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \nonumber \\
	D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \label{eq:effects} \\
	M(A) &= \exp( -T^2 / 2 ) A, \nonumber
\end{align}
with the four dimensionless parameters,
\begin{equation}
	\begin{aligned}
		a &= \exp( g_0 L_g ) \sim 8 \times 10^3, & 
		h &= (1 - R) \exp( - \alpha L_T) \sim 0.04, \\
		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, & s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2,
		\label{eq:ndparam}
	\end{aligned}
\end{equation}
as defined by the values in Table~\ref{tab:values}. Here, $a$ is a measure of the strength of the gain fibre, $h$ is the loss due to absorption and the output coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse. Furthermore, notice that in this non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:ndparam} have their own independent, non-dimensional parameter.

@@

Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity. Unlike the models models described in the beginning of this section, the permutation of our components is important as the maps \eqref{eq:effects} do not commute with each other. Furthermore, the order of the components will be dictated by the geometry of a particular laser, however, we the laser is constructed as in Fig.~\ref{fig:cavity},  with the following justifications. The effect of the nonlinearity will me maximized after the pulse passes through the gain fibre---this is the region where the pulse is most energetic. Thus, we take the nonlinearity component to follow the gain. Similarly, we would want the loss component to directly follow the nonlinearity in an attempt to minimize the effect the nonlinearity has on the pulse. This leaves the dispersion and modulation components. For now, let us assume the CFBG precedes the modulator. Finally, we assume the loss component is our reference point since this corresponds to the output coupler, and thus, the point in the cavity we are able to take our measurements. More precisely, let
\begin{align}
	\mathcal{L}(A) = F(G(M(D(L(A)))))
	\label{eq:order}
\end{align}
denote one complete round trip of the cavity. Since a ring laser is cyclic in nature, we use the result of one round trip as the input pulse for the next round trip---restarting the process. We continually repeat this procedure until the envelope and chirp of the pulse reaches equilibrium, or the pulse degrades due to modulation instability. Note that we are uninterested in the phase change as it is not modified by the maps in a meaningful way, and due to the nature of experimental measurements. An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.

@@

\subsection{Linear Solution}
By neglecting the effect of the nonlinearity, that is, $b = 0$, a solution can be found analytically. We proceed by assuming a fixed point will take the form of a linearly chirped Gaussian. There are a few reasons for this; the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform. Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.

@@

\begin{figure*}[tbp]
	\centering
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/Chirp}
		\caption{Chirp.}
		\label{fig:chirp}
	\end{subfigure} %
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/FT}
		\caption{Fourier transform.}
		\label{fig:ft}
	\end{subfigure}
	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for two values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
	\label{fig:chirpft}
\end{figure*}

@@

@@

%The authors would like to thank O. Aytür for critical reading of the manuscript
